### 2021-01-25 doc/manuscript/Dow_manuscript_Nature.Rmd
add some refs

As the climate changes, warmer spring temperatures are causing earlier leaf-out[REFS] and commencement of net carbon dioxide (CO~2~) sequestration[REFS] in temperate deciduous forests, resulting in a tendency towards increased growing season length[REFS] and annual CO~2~ sequestration[REFS].
However, little is known about how spring temperatures affect tree stem growth, which consumes a modest portion of the carbon fixed annually[REFS] but is the longest-lived carbon sink[REFS].
Here, we show that in two temperate deciduous forests, warmer maximum spring temperatures consistently shifted *both leaf phenology* and woody growth milestones earlier but had mixed, weak effects on peak growing season length, maximum daily growth rates, and annual growth.
*The latter finding is confirmed on the centennial scale by tree-ring records across # forests.*
These findings are consistent with *~~most tree-ring studies in temperate deciduous forests showing that annual growth tends to be more sensitive to climatic conditions during the peak growing season than in the spring[REFS], with~~* eddy-covariance records showing that annual CO~2~ sequestration is more strongly linked to conditions in the peak growing season than to growing season length[@fu_maximum_2019], with *previous* observations that warm springs result in earlier leaf senescence[@zohner_ongoing_2019; @zani_increased_2020], and with evidence that forest CO~2~ sequestration is sink-limited[@zani_increased_2020].
They contrast, however, with the expectation *in most models[@zani_increased_2020]* that an earlier start to growing season would significantly increase the rate of biomass accumulation and thereby enhance the CO~2~ sink of temperate deciduous forests, implying that warming spring conditions are unlikely to impact temperate deciduous forest growth sufficiently to produce any substantial negative climate change feedback.

>>>>

As the climate changes, warmer spring temperatures are causing earlier leaf-out[REFS] and commencement of net carbon dioxide (CO~2~) sequestration[REFS] in temperate deciduous forests, resulting in a tendency towards increased growing season length[@menzel_growing_1999;@menzel_european_2006;@ibanez_forecasting_2010;@jeong_phenology_2011] and annual CO~2~ sequestration[@keeling_increased_1996;@dragoni_evidence_2011;@crabbe_extreme_2016].
However, little is known about how spring temperatures affect tree stem growth, which consumes a modest portion of the carbon fixed annually[REFS] but is the longest-lived carbon sink[REFS].
Here, we show that in two temperate deciduous forests, warmer maximum spring temperatures consistently shifted *both leaf phenology* and woody growth milestones earlier but had mixed, weak effects on peak growing season length, maximum daily growth rates, and annual growth.
*The latter finding is confirmed on the centennial scale by tree-ring records across # forests.*
These findings are consistent with *~~most tree-ring studies in temperate deciduous forests showing that annual growth tends to be more sensitive to climatic conditions during the peak growing season than in the spring[REFS], with~~* eddy-covariance records showing that annual CO~2~ sequestration is more strongly linked to conditions in the peak growing season than to growing season length[@fu_maximum_2019], with *previous* observations that warm springs result in earlier leaf senescence[@zohner_ongoing_2019; @zani_increased_2020], and with evidence that forest CO~2~ sequestration is sink-limited[@zani_increased_2020].
They contrast, however, with the expectation *in most models[@zani_increased_2020]* that an earlier start to growing season would significantly increase the rate of biomass accumulation and thereby enhance the CO~2~ sink of temperate deciduous forests, implying that warming spring conditions are unlikely to impact temperate deciduous forest growth sufficiently to produce any substantial negative climate change feedback.
